Project

### 2018-11-22 project.Rmd
chn

*  Focus on holistic coaching, 
*  Embody best practices from the writing in the disciplines literature
*  Can be implemented at large scale by less experienced teaching assistants
*  Focus student and instructor attention on larger issues rather than simple copy-correction.

>>>>

*  Focus on holistic coaching 
*  Embody best practices from the writing in the disciplines literature
*  Can be implemented at large scale by less experienced teaching assistants
*  Focus student and instructor attention on larger issues rather than simple copy-correction.
